\section{Licensing and Acknowledgements} \label{licensing}

    CEL (Camera Evaluation Language) is a research project by Marc Christie (\href{http://www.inria.fr}{INRIA-Rennes}, France), Roberto Ranon and Tommaso Urli (both from HCI-Lab, \href{http://www.uniud.it}{University of Udine}, Italy), for the latest info see \href{http://www.cameracontrol.org/language}{www.cameracontrol.org/language}. If you use, modify, or simply find this code interesting please let us know at \href{mailto:info@cameracontrol.org}{info@cameracontrol.org}.
    
    %Copyright \copyright~ 2010 INRIA Rennes, France and University of Udine, Italy. 
    
    This program is free software; you can redistribute it and/or modify it under the terms of the GNU Lesser General Public License as published by the Free Software Foundation; either version 2 of the License, or (at your option) any later version. You should have received a copy of the GNU Lesser General Public License along with this program; if not, write to the Free Software Foundation, Inc., 59 Temple Place - Suite 330, Boston, MA 02111-1307, USA, or go to \href{http://www.gnu.org/copyleft/lesser.txt}{www.gnu.org/copyleft/lesser.txt}.
    
    This program is distributed in the hope that it will be useful, but WITHOUT ANY WARRANTY; without even the implied warranty of MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE. See the GNU Lesser General Public License for more details. 
    
    Details about CEL's licensing are included at the top of every source file.

    \subsection{Ogre}
    
        A fundamental part of CEL relies on Ogre rendering engine (\href{http://www.ogre3d.org}{www.ogre3d.org}) and our most sincere thanks go to the Ogre community and Torus Knot Software, for developing such a great piece of software. At the current moment, we are not redistributing any of the code from Ogre project and we don't take any responsibility about its licensing. Read more about this topic at \href{http://www.ogre3d.org/licensing}{www.ogre3d.org/licensing} before installing or redistributing it.
        
    \subsection{OgreMax}
        
        Portions of this work is provided by OgreMax (\href{http://www.ogremax.com}{www.ogremax.com}), OgreMax was written by Derek Nedelman. Derek Nedelman assumes no responsibility for any harm caused by using this code.
        
    \subsection{TinyXML}
    
        OgreMax makes use of TinyXML, an open-source piece of software which is used to parse and visit XML documents. TinyXML is currently maintained by Lee Thomason (\href{http://www.grinninglizard.com}{www.grinninglizard.com}).

    \subsection{Included city scene}

    The example scene depicting portion of a city was modeled by Guy Schofield from Culture Lab, Newcastle, UK.
    
